Online Verification of Commutativity

### 2020-10-05 acmPaper/paper.tex
Tweaking algorithm listings

Graph existingGraph\;
$R_s$ $\gets$ \{\}\;
\ForEach{node v in V}{
    S $\gets$ existingGraph.extractReachableSection(v)\;
    T $\gets$ createMinimumSpanningTree(S)\;
    excludedEdges = S.edges - T.edges\;
    \ForEach{edge e $\in$ excludedEdges}{
        firstPath = T.findPath(source: e.source, sink: e.sink)\;
        $R_s$.addElement(new Bilinking(firstPath, e)\;
    } 
}
\KwRet{$R_s$}\;

\caption{Finding a spanning set.}\label{algo_spanning_set}
\end{algorithm}

@@

\begin{algorithm}[t]
\DontPrintSemicolon
\KwResult{Find a minimal spanning set R.}

\SetKwFunction{FSigma}{$\sigma$}
\SetKwProg{Fn}{Function}{:}{}
\Fn{\FSigma{inputSet S, codomain Rs}}{
    output $\gets$ \{\}\;
    \For{bilinking $\in$ Rs}{
        \tcc{Get fragments that could build up to the bilinking.}
        smallerPairs $\gets$ getSmallerPairs(bilinking)\;
        consideredPieces $\gets$ smallerPairs $\cap$ S \;
        \tcc{See if bilinking can be built from these pieces.}
        \If{linearlyDependent(consideredPieces, bilinking)}{
            output.add(bilinking)\;
        }
    }
    \KwRet{output}
}

@@

parallelPairs $\gets$ \{\}\;
\For{S in existingGraph.Nodes}{
    \For{T in existingGraph}{
        \try{}{
            Path pathWithNewEdge $\gets$ FindPath(
                graph: existingGraph, 
                sourceNode: S,
                sinkNode: newEdge.Source()) +\;
            newEdge as Path +\;
            FindPath(
                graph: existingGraph, 
                sourceNode: newEdge.Sink(), 
                sinkNode: T)\;
            \If{S == T}{
                pathInOldGraph $\gets$ identity(S)\;
            }
            \Else(){
                Path pathInOldGraph $\gets$ FindPath(
                    graph: existingGraph, 
                    sourceNode: S, 
                    sinkNode: T)\;
            }
            parallelPairs.add((pathInOldGraph, pathWithNewEdge))\;
        }
        \catch{PathFindingFailedException}{
           \tcc{No comparable pairs from node S to node T that need to be checked}
           continue\;
        }
    }
}
\KwRet{parallelPairs}\;
\caption{Online polynomial time algorithm to find parallel pair set}
\label{algo_online_polynomial}
\end{algorithm}

@@

predecessors $\gets$ S.predecessors(existingGraph)\;
successors $\gets$ T.successors(existingGraph)\;

Graph terminalPairGraph\;
\For{q $\in$ successors}{
    \For{p $\in$ predecessors}{
        terminalPairGraph.addNode(q, p)\;
        \For{qPred $\in$ q.predecessors(existingGraph)}{
            \For{pSucc $\in$ p.successors(existingGraph)}{
                terminalPairGraph.addEdge((qPred, pSucc))\;
            }
        }
    }
}

verificationSet $\gets$ \{\}\;
\While{len(terminalPairGraph.nodes) $>$ 0}{
    currentNode $\gets$ terminalPairGraph.nodes[0]\;
    visitedNodes $\gets$ \{\}\;
    \While{len(currentNode.parents()) $>$ 0}{
        visitedNodes.add(currentNode)\;
        currentNode $\gets$ currentNode.parents()[0]\;
        \If{currentNode $\in$ visitedNodes}{
            edges $\gets$ getAllEdges(visitedNodes, terminalPairGraph)\;
            terminalPairGraph.removeNodes(visitedNodes)\;
            terminalPairGraph.addNode(currentNode, edges)\; 
        }
    }
    verificationSet.add(currentNode)\;
    terminalPairGraph.removeNodes( currentNode.successors(terminalPairGraph))\;
}
\KwRet{verificationSet}\;
\caption{Minimal set finding algorithm}
\label{algo_online_minimal}
\end{algorithm}

>>>>

Graph existingGraph\;
$R_s$ $\gets$ \{\}\;
\ForEach{node v in V}{
    S $\gets$ existingGraph.extractReachableSection(v)\;
    T $\gets$ createMinimumSpanningTree(S)\;
    excludedEdges = edges in subgraph S - edges in T\;
    \ForEach{edge e $\in$ excludedEdges}{
        firstPath = T.findPath(source: e.source, sink: e.sink)\;
        $R_s$.addElement((firstPath, e))\;
    } 
}
\KwRet{$R_s$}\;

\caption{Finding a spanning set of path pairs.}\label{algo_spanning_set}
\end{algorithm}

@@

\begin{algorithm}[t]
\DontPrintSemicolon
\KwResult{Find a minimal spanning set of path pairs (bilinkings) R.}

\SetKwFunction{FSigma}{$\sigma$}
\SetKwProg{Fn}{Function}{:}{}
\Fn{\FSigma{input set S, spanning set Rs}}{
    output $\gets$ \{\}\;
    \For{bilinking $\in$ Rs}{
        \tcc{Get fragments that could build up to the bilinking. Corresponds to applying <> function.}
        smallerPairs $\gets$ allShorterPieces(bilinking)\;
        consideredPieces $\gets$ smallerPairs $\cap$ S \;
        \tcc{Now see if bilinking can be built from these pieces.}
        \If{linearlyDependent(consideredPieces, bilinking)}{
            output.add(bilinking)\;
        }
    }
    \KwRet{output}
}

@@

parallelPairs $\gets$ \{\}\;
\For{src in existingGraph.Nodes}{
    \For{snk in existingGraph}{
        \try{}{
            Path pathWithNewEdge $\gets$ FindPath(
                % graph: existingGraph, 
                sourceNode: src,
                sinkNode: newEdge.Source +\;
            newEdge as Path +\;
            FindPath(
                % graph: exisingGraph, 
                sourceNode: newEdge.Sink, 
                sinkNode: snk)\;
            \If{src == snk}{
                pathInOldGraph $\gets$ identity(src)\;
            }
            \Else(){
                Path pathInOldGraph $\gets$ FindPath(
                    % graph: existingGraph, 
                    sourceNode: src, 
                    sinkNode: snk)\;
            }
            parallelPairs.add((pathInOldGraph, pathWithNewEdge))\;
        }
        \catch{PathFindingFailedException}{
           \tcc{No comparable pairs from node src to node snk that need to be checked}
           continue\;
        }
    }
}
\KwRet{parallelPairs}\;
\caption{Online polynomial time algorithm to find parallel pair set}
\label{algo_online_polynomial}
\end{algorithm}

@@

predecessors $\gets$ predecessors of S in existingGraph\;
successors $\gets$ successors of T in existingGraph\;

Graph terminalPairGraph $\gets$ empty \;
\For{q $\in$ successors}{
    \For{p $\in$ predecessors}{
        terminalPairGraph.addNode((q, p))\;
        \For{predecessor $\in$ predecessors of q in existingGraph}{
            \For{successor $\in$ predecessors of p in existingGraph}{
                terminalPairGraph.addEdge((predecessor, successor))\;
            }
        }
    }
}

verificationSet $\gets$ \{\}\;
\While{terminalPairGraph.nodes not empty}{
    currentNode $\gets$ terminalPairGraph.node\;
    \tcp*{an arbitrarily chosen node of terminalPairGraph}
    \While{currentNode has predecessors}{
        currentNode $\gets$ predecessor\;
        \tcp*{an arbitrarily chosen predecessor of current Node}
    }
    verificationSet.add(currentNode)\;
    terminalPairGraph.removeAllSuccessors(currentNode)\;
}
\KwRet{verificationSet}\;
\caption{Minimal set finding algorithm}
\label{algo_online_minimal}
\end{algorithm}
